### 2022-12-02 definitions.tex
details

\begin{proposition}
{\sc $k$-resilience}, hence {\sc bounded resilience} and {\sc resilience}, is undecidable for effective WSTS with strong upward compatibility ????
\end{proposition}

>>>>

\begin{proposition}
({\sc $k$-resilience},) hence {\sc bounded resilience}, is undecidable for effective WSTS with strong upward compatibility ????
\end{proposition}
